---
title: 'make map with R '
author: "BENADROUCHE Kamila"
date: "01/12/2020"
output:
  html_document: default
  word_document: default
---

##map of the hosipitls of algiers (Algeria)


## The leaflet package

install.packages("leaflet ")
```{r}
library(leaflet)
```

##create the map
```{r}
leaflet()
```
##add a label to the map
```{r}
leaflet()%>%addTiles
```
##Display the different labels provided by providers

```{r}
names(providers)
```

##Centralize my card in Algiers
I centralize my map in Algiers using the setView function
to do that I need the GPS coordinates of Algiers (lng: longitude and lat: latitude). 
```{r}
leaflet()%>%addProviderTiles("CartoDB")%>%setView(lng=3.0601882,lat=36.7753606,zoom=12)
```
##save my map in an object called map_alger

I'll create an object and name it map_alger to save our map
```{r}
map_alger<-leaflet(option=leafletOptions(minZoom =12 ))%>%addProviderTiles("CartoDB")%>%setView(lng =3.0601882 , lat = 36.7753606, zoom = 13)
map_alger
```

##Load data
To load our data we use the tidyverse package.
Install.packages (tidyverse) for the installation of the tidyverse package
```{r}
library(tidyverse)
```


```{r}
library(readxl)
donnees<-read_excel("liste des hopiteaux.xlsx")
```
##Clean the data
```{r}
donnees<-drop_na(donnees,lon)
donnees
```
```{r}
donnees$lon<-as.numeric(donnees$lon)
donnees$lat<-as.numeric(donnees$lat)



```

##add markers
```{r}
map_alger%>%addMarkers(lng=donnees$lon, lat=donnees$lat, popup=donnees$Hopital)
```



```{r}
map_alger%>%addMarkers(lng=donnees$lon, lat=donnees$lat, popup = donnees$Hopital)
```

